\chapter{Numbers 30}
%[cmyk]{0.99998,1,0,0}{

\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{RASH DECISIONS}}\\ (Numbers 30)
\begin{compactenum}[I.][8]
    \item A \textbf{Vow}   \index[scripture]{Numbers!Num 30:02}\index[scripture]{Numbers!Num 30:03}\index[scripture]{Numbers!Num 30:04}\index[scripture]{Numbers!Num 30:06}\index[scripture]{Numbers!Num 30:08}\index[scripture]{Numbers!Num 30:09}\index[scripture]{Numbers!Num 30:12}\index[scripture]{Numbers!Num 30:13}\index[scripture]{Numbers!Num 30:14}\index[scripture]{Numbers!Num 30:15}  (Numbers 30:2, 3, 4, 6, 8, 9, 12, 13, 14, 15)  
    \item  \textbf{Voiding}   \index[scripture]{Numbers!Num 30:12}\index[scripture]{Numbers!Num 30:13} (Numbers 30:12, 13)  
    \item  The \textbf{Value}  of One's Word %\index[scripture]{Numbers!Num 30:12}\index[scripture]{Numbers!Num 30:13} (Numbers 30:12, 13)  
    \item  The \textbf{Validity}  of a Promise %\index[scripture]{Numbers!Num 30:12}\index[scripture]{Numbers!Num 30:13} (Numbers 30:12, 13)  
\end{compactenum}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\footnote{\textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{NumbersTOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/numbers_30.html}{\textcolor[cmyk]{0.99998,1,0,0}{Numbers 30 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{And Moses spake unto the heads of the tribes concerning the children of Israel, saying, This \emph{is} the thing which the LORD hath commanded.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{If a man vow a vow unto the LORD, or swear an oath to bind his soul with a bond; he shall not break his word, he shall do according to all that proceedeth out of his mouth.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{If a woman also vow a vow unto the LORD, and bind herself by a bond, \emph{being} in her father's house in her youth;}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And her father hear her vow, and her bond wherewith she hath bound her soul, and her father shall hold his peace at her: then all her vows shall stand, and every bond wherewith she hath bound her soul shall stand.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{But if her father disallow her in the day that he heareth; not any of her vows, or of her bonds wherewith she hath bound her soul, shall stand: and the LORD shall forgive her, because her father disallowed her.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{And if she had at all an husband, when she vowed, or uttered ought out of her lips, wherewith she bound her soul;}
[7] \textcolor[cmyk]{0.99998,1,0,0}{And her husband heard \emph{it,} and held his peace at her in the day that he heard \emph{it}: then her vows shall stand, and her bonds wherewith she bound her soul shall stand.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{But if her husband disallowed her on the day that he heard \emph{it}; then he shall make her vow which she vowed, and that which she uttered with her lips, wherewith she bound her soul, of none effect: and the LORD shall forgive her.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{But every vow of a widow, and of her that is divorced, wherewith they have bound their souls, shall stand against her.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{And if she vowed in her husband's house, or bound her soul by a bond with an oath;}
[11] \textcolor[cmyk]{0.99998,1,0,0}{And her husband heard \emph{it}, and held his peace at her, \emph{and} disallowed her not: then all her vows shall stand, and every bond wherewith she bound her soul shall stand.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{But if her husband hath utterly made them void on the day he heard \emph{them;} \emph{then} whatsoever proceeded out of her lips concerning her vows, or concerning the bond of her soul, shall not stand: her husband hath made them void; and the LORD shall forgive her.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{Every vow, and every binding oath to afflict the soul, her husband may establish it, or her husband may make it void.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{But if her husband altogether hold his peace at her from day to day; then he establisheth all her vows, or all her bonds, which \emph{are} upon her: he confirmeth them, because he held his peace at her in the day that he heard \emph{them}.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{But if he shall any ways make them void after that he hath heard \emph{them}; then he shall bear her iniquity.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{These \emph{are} the statutes, which the LORD commanded Moses, between a man and his wife, between the father and his daughter, \emph{being} \emph{yet} in her youth in her father's house.}