\subsection{Outlines from Eades}

\subsubsection{Don't give up on the mountain}
%\textbf{Introduction:} Psalm 2:\footnote{8 June 2016, Keith Anthony}
\index[speaker]{Brian Eades!Psalm 042 (Don't give up on the mountain)}
\index[series]{Psalms (Brian Eades)!Psalm 042 (Don't give up on the mountain)}
\index[date]{2020/09/17!Psalm 042 (Don't give up on the mountain) (Brian Eades)}

\index[FACEBOOK]{SERMON HIINTS!Brian Eades (Don't give up on the mountain) - Psalm 42 (2020/09/17)}
\textbf{INTRODUCTION: } Numbers 13:30 (KJV)  And Caleb stilled the people before Moses, and said, Let us go up at once, and possess it; for we are well able to overcome it.
Joshua 14:11-12 (KJV)  As yet I am as strong this day as I was in the day that Moses sent me: as my strength was then, even so is my strength now, for war, both to go out, and to come in.
Now therefore give me this mountain, whereof the LORD spake in that day; for thou heardest in that day how the Anakims were there, and that the cities were great and fenced: if so be the LORD will be with me, then I shall be able to drive them out, as the LORD said.
Not everybody can say what Caleb said as an 85 year old man. Basically said "I've still got it"!  Because of the unbelief of others, Caleb had to wait 40 long years going in circles in the wilderness, until he finally claimed the mountain for himself and his family.
Caleb is mentioned by name 37 times in Scripture. He and Joshua were the only two that walked out of Egypt into the Promised Land! All of the rest including Moses died in the wilderness except those born in the wilderness.
\begin{compactenum}[I.][19]
    \item Caleb was a spying man
(The Grapes of Eshcol)
    \item Caleb was a spiritual man
("We are able")
    \item Caleb was a stable man
(40 long years of consistent faith)
    \item Caleb was a strengthening man (he strengthened his daughters by his faith and words of encouragement)
\end{compactenum}


