\chapter{Numbers 23}

%[cmyk]{0.99998,1,0,0}{

\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{ATTEMPT TO CURSE ISRAEL}}\\ (Numbers 23)
\begin{compactenum}[I.][8]
   \item A \textbf{Nation set Apart} \index[scripture]{Numbers!Num 23:09} (Numbers 23:9)
    \item A \textbf{Nation Protected} \index[scripture]{Numbers!Num 23:09} (Numbers 23:9)
    \item A \textbf{Nation Preferred} \index[scripture]{Numbers!Num 23:09} (Numbers 23:9)
    \item A \textbf{Notable Parable} \index[scripture]{Numbers!Num 23:07} (Numbers 23:7)
    \item A \textbf{Notion that is Poisonous} (to prefer what God prefers) \index[scripture]{Numbers!Num 23:11} (Numbers 23:11)
    \item The \textbf{Nagging Problem} \index[scripture]{Numbers!Num 23:12} (Numbers 23:12)
    \begin{compactenum}[A.][8]
    	\item Balak could not get the solution he wanted, despite co--opting religion
        \item Israel holds a special and protected place, a place enforced by God Himself.
        \item Cannot curse what God has blessed
    \end{compactenum}\end{compactenum}}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\footnote{\textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{NumbersTOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/numbers_23.html}{\textcolor[cmyk]{0.99998,1,0,0}{Numbers 23 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{Balaam} said unto Balak, Build me here seven altars, and prepare me here seven oxen and seven rams.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And Balak did as \fcolorbox{bone}{bone}{Balaam} had spoken; and Balak and \fcolorbox{bone}{bone}{Balaam} offered on \emph{every} altar a bullock and a ram.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{Balaam} said unto Balak, Stand by thy burnt offering, and I will go: peradventure the LORD will come to meet me: and whatsoever he sheweth me I will tell thee. And he went to an high place.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And God met \fcolorbox{bone}{bone}{Balaam}: and he said unto him, I have prepared seven altars, and I have offered upon \emph{every} altar a bullock and a ram.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD put a word in Balaam's mouth, and said, Return unto Balak, and thus thou shalt speak.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{And he returned unto him, and, lo, he stood by his burnt sacrifice, he, and all the princes of Moab.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{And he took up his parable, and said, Balak the king of Moab hath brought me from Aram, out of the mountains of the east, \emph{saying}, Come, curse me Jacob, and come, defy Israel.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{How shall I curse, whom God hath not cursed? or how shall I defy, \emph{whom} the LORD hath not defied?}
[9] \textcolor[cmyk]{0.99998,1,0,0}{For from the top of the rocks I see him, and from the hills I behold him: lo, the people shall dwell alone, and shall not be reckoned among the nations.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{Who can count the dust of Jacob, and the number of the fourth \emph{part} of Israel? Let me die the death of the righteous, and let my last end be like his!}
[11] \textcolor[cmyk]{0.99998,1,0,0}{And Balak said unto \fcolorbox{bone}{bone}{Balaam}, What hast thou done unto me? I took thee to curse mine enemies, and, behold, thou hast blessed \emph{them} altogether.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{And he answered and said, Must I not take heed to speak that which the LORD hath put in my mouth?}
[13] \textcolor[cmyk]{0.99998,1,0,0}{And Balak said unto him, Come, I pray thee, with me unto another place, from whence thou mayest see them: thou shalt see but the utmost part of them, and shalt not see them all: and curse me them from thence.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And he brought him into the field of Zophim, to the top of Pisgah, and built seven altars, and offered a bullock and a ram on \emph{every} altar.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{And he said unto Balak, Stand here by thy burnt offering, while I meet \emph{the} \emph{LORD} yonder.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD met \fcolorbox{bone}{bone}{Balaam}, and put a word in his mouth, and said, Go again unto Balak, and say thus.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{And when he came to him, behold, he stood by his burnt offering, and the princes of Moab with him. And Balak said unto him, What hath the LORD spoken?}
[18] \textcolor[cmyk]{0.99998,1,0,0}{And he took up his parable, and said, Rise up, Balak, and hear; hearken unto me, thou son of Zippor:}
[19] \textcolor[cmyk]{0.99998,1,0,0}{God \emph{is} not a man, that he should lie; neither the son of man, that he should repent: hath he said, and shall he not do \emph{it}? or hath he spoken, and shall he not make it good?}
[20] \textcolor[cmyk]{0.99998,1,0,0}{Behold, I have received \emph{commandment} to bless: and he hath blessed; and I cannot reverse it.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{He hath not beheld iniquity in Jacob, neither hath he seen perverseness in Israel: the LORD his God \emph{is} with him, and the shout of a king \emph{is} among them.}
[22] \textcolor[cmyk]{0.99998,1,0,0}{God brought them out of Egypt; he hath as it were the strength of an unicorn.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{Surely \emph{there} \emph{is} no enchantment against Jacob, neither \emph{is} \emph{there} any divination against Israel: according to this time it shall be said of Jacob and of Israel, What hath God wrought!}
[24] \textcolor[cmyk]{0.99998,1,0,0}{Behold, the people shall rise up as a great lion, and lift up himself as a young lion: he shall not lie down until he eat \emph{of} the prey, and drink the blood of the slain.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Balak said unto \fcolorbox{bone}{bone}{Balaam}, Neither curse them at all, nor bless them at all.}
[26] \textcolor[cmyk]{0.99998,1,0,0}{But \fcolorbox{bone}{bone}{Balaam} answered and said unto Balak, Told not I thee, saying, All that the LORD speaketh, that I must do?}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Balak said unto \fcolorbox{bone}{bone}{Balaam}, Come, I pray thee, I will bring thee unto another place; peradventure it will please God that thou mayest curse me them from thence.}
[28] \textcolor[cmyk]{0.99998,1,0,0}{And Balak brought \fcolorbox{bone}{bone}{Balaam} unto the top of Peor, that looketh toward Jeshimon.}
[29] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{Balaam} said unto Balak, Build me here seven altars, and prepare me here seven bullocks and seven rams.}
[30] \textcolor[cmyk]{0.99998,1,0,0}{And Balak did as \fcolorbox{bone}{bone}{Balaam} had said, and offered a bullock and a ram on \emph{every} altar.}