\chapter{Numbers 14}



\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{THE LAST STRAW}}\\ (Numbers 14:1-45) \begin{compactenum}[I.][8]
    \item \textbf{More Complaints} \index[scripture]{Numbers!Num 14:02} (Numbers 14:2) 
    \item \textbf{Murmuring Citizens} \index[scripture]{Numbers!Num 14:02} (Numbers 14:2) 
    \item \textbf{Moses (and Aaron) Contrite} \index[scripture]{Numbers!Num 14:05} (Numbers 14:5) 
    \item \textbf{Miracles \fcolorbox{bone}{bone}{not} Considered} \index[scripture]{Numbers!Num 14:23} (Numbers 14:23) 
    \item \textbf{Many Condemned} \index[scripture]{Numbers!Num 14:23} (Numbers 14:23) 
    \item \textbf{Many Carcasses} \index[scripture]{Numbers!Num 14:29}\index[scripture]{Numbers!Num 14:33} (Numbers 14:29, 33) 
    \item \textbf{Mourning Commences} \index[scripture]{Numbers!Num 14:23} (Numbers 14:23) 
    \item \textbf{Military Catastrophe} \index[scripture]{Numbers!Num 14:45} (Numbers 14:45)
\end{compactenum}}


\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/numbers_14.html}{\textcolor[cmyk]{0.99998,1,0,0}{Numbers 14 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{all} the congregation lifted up their voice, and cried; and the people wept \fcolorbox{bone}{bone}{that}  night.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{all} the children of Israel \fcolorbox{bone}{lime}{murmured} against Moses and against Aaron: and the whole congregation said unto them, \fcolorbox{bone}{lime}{Would God} \fcolorbox{bone}{bone}{that}  we had died in \fcolorbox{bone}{bone}{the land} of Egypt! or would God we had died in this wilderness!}
[3] \textcolor[cmyk]{0.99998,1,0,0}{And wherefore hath the LORD brought us unto this land, to fall by the sword, \fcolorbox{bone}{bone}{that}  our wives and our children should be a prey? were it \fcolorbox{bone}{bone}{not} better for us to return into Egypt?}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And they said one to another, Let us make a captain, and let us return into Egypt.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{Then \fcolorbox{bone}{lime}{Moses and Aaron} fell on their faces before \fcolorbox{bone}{bone}{all} the assembly of the congregation of the children of Israel.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Joshua the son of Nun, and Caleb the son of Jephunneh, \emph{which} \emph{were} of them \fcolorbox{bone}{bone}{that}  searched \fcolorbox{bone}{bone}{the land}, rent their clothes:}
[7] \textcolor[cmyk]{0.99998,1,0,0}{And they spake unto \fcolorbox{bone}{bone}{all} the company of the children of Israel, saying, The land, which we passed through to search it, \emph{is} an exceeding good land.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{If the LORD delight in us, then he \fcolorbox{bone}{bone}{will} bring us into this land, and give it us; a land which floweth with milk and honey.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{Only rebel \fcolorbox{bone}{bone}{not} \fcolorbox{bone}{bone}{ye} against the LORD, neither fear \fcolorbox{bone}{bone}{ye} the people of \fcolorbox{bone}{bone}{the land}; for they \emph{are} bread for us: their defence is departed from them, and the LORD \emph{is} with us: fear them not.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{But \fcolorbox{bone}{bone}{all} the congregation bade stone them with stones. And the glory of the LORD appeared in the tabernacle of the congregation before \fcolorbox{bone}{bone}{all} the children of Israel.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And the LORD said unto Moses, How long \fcolorbox{bone}{bone}{will} this people provoke me? and how long \fcolorbox{bone}{bone}{will} it be ere they believe me, for \fcolorbox{bone}{bone}{all} the signs which I have shewed among them?}
[12] \textcolor[cmyk]{0.99998,1,0,0}{I \fcolorbox{bone}{bone}{will} smite them with the pestilence, and disinherit them, and \fcolorbox{bone}{bone}{will} make of thee a greater nation and mightier than they.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Moses said unto the LORD, Then the Egyptians shall hear \emph{it}, (for thou broughtest up this people in thy might from among them;)}
[14] \textcolor[cmyk]{0.99998,1,0,0}{And they \fcolorbox{bone}{bone}{will} tell \emph{it} to the inhabitants of this land: \emph{for} they have heard \fcolorbox{bone}{bone}{that}  thou LORD \emph{art} among this people, \fcolorbox{bone}{bone}{that}  thou LORD art seen face to face, and \emph{that} thy cloud standeth over them, and \emph{that} thou goest before them, by day time in a pillar of a cloud, and in a pillar of fire by night.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Now \emph{if} thou shalt kill \emph{all} this people as one man, then the nations which have heard the fame of thee \fcolorbox{bone}{bone}{will} speak, saying,}
[16] \textcolor[cmyk]{0.99998,1,0,0}{Because the LORD was \fcolorbox{bone}{bone}{not} able to bring this people into \fcolorbox{bone}{bone}{the land} which he sware unto them, therefore he hath slain them in the wilderness.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{And now, I beseech thee, let the power of my Lord be great, according as thou hast spoken, saying,}
[18] \textcolor[cmyk]{0.99998,1,0,0}{The LORD \emph{is} \fcolorbox{bone}{MYGOLD}{longsuffering}, and of great mercy, forgiving iniquity and \fcolorbox{bone}{MYGOLD}{transgression}, and by no means clearing \emph{the} \emph{guilty}, visiting the iniquity of the fathers upon the children unto the third and fourth \emph{generation}.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{Pardon, I beseech thee, the iniquity of this people according unto the greatness of thy mercy, and as thou hast forgiven this people, from Egypt even until now.}
[20] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD said, I have pardoned according to thy word:}
[21] \textcolor[cmyk]{0.99998,1,0,0}{But \emph{as} truly \emph{as} I live, \fcolorbox{bone}{bone}{all} the earth shall be filled with the glory of the LORD.}
[22] \textcolor[cmyk]{0.99998,1,0,0}{Because \fcolorbox{bone}{bone}{all} those men which have seen my glory, and my miracles, which I did in Egypt and in the wilderness, and have tempted me now these ten times, and have \fcolorbox{bone}{bone}{not} hearkened to my voice;}
[23] \textcolor[cmyk]{0.99998,1,0,0}{Surely they \fcolorbox{bone}{lime}{shall \fcolorbox{bone}{bone}{not} see} \fcolorbox{bone}{bone}{the land} which I sware unto their fathers, \fcolorbox{bone}{lime}{neither shall} any of them \fcolorbox{bone}{bone}{that}  provoked me see it:}
[24] \textcolor[cmyk]{0.99998,1,0,0}{But my servant Caleb, because he had another spirit with him, and hath followed me fully, him \fcolorbox{bone}{bone}{will} I bring into \fcolorbox{bone}{bone}{the land} whereinto he went; and his seed shall possess it.}
[25] \textcolor[cmyk]{0.99998,1,0,0}{(Now the Amalekites and the Canaanites dwelt in the valley.) To morrow turn you, and get you into the wilderness by the way of the Red sea.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And the LORD spake unto Moses and unto Aaron, saying,}
[27] \textcolor[cmyk]{0.99998,1,0,0}{How long \emph{shall} \emph{I} \emph{bear} \emph{with} this evil congregation, which murmur against me? I have heard the murmurings of the children of Israel, which they murmur against me.}
[28] \textcolor[cmyk]{0.99998,1,0,0}{Say unto them, \emph{As} \emph{truly} \emph{as} I live, saith the LORD, as \fcolorbox{bone}{bone}{ye} have spoken in mine ears, so \fcolorbox{bone}{bone}{will} I do to you:}
[29] \textcolor[cmyk]{0.99998,1,0,0}{Your \fcolorbox{bone}{lime}{carcases} shall fall in this wilderness; and \fcolorbox{bone}{bone}{all} \fcolorbox{bone}{bone}{that}  were numbered of you, according to your whole number, from twenty years old and upward, which have murmured against me,}
[30] \textcolor[cmyk]{0.99998,1,0,0}{Doubtless \fcolorbox{bone}{bone}{ye} shall \fcolorbox{bone}{bone}{not} come into \fcolorbox{bone}{bone}{the land}, \emph{concerning} which I sware to make you dwell therein, save Caleb the son of Jephunneh, and Joshua the son of Nun.}
[31] \textcolor[cmyk]{0.99998,1,0,0}{But your little ones, which \fcolorbox{bone}{bone}{ye} said should be a prey, them \fcolorbox{bone}{bone}{will} I bring in, and they shall know \fcolorbox{bone}{bone}{the land} which \fcolorbox{bone}{bone}{ye} have despised.}
[32] \textcolor[cmyk]{0.99998,1,0,0}{But \emph{as} \emph{for} you, your carcases, they shall fall in this wilderness.}
[33] \textcolor[cmyk]{0.99998,1,0,0}{And your children shall wander in the wilderness forty years, and bear your whoredoms, until your carcases be wasted in the wilderness.}
[34] \textcolor[cmyk]{0.99998,1,0,0}{After the number of the days in which \fcolorbox{bone}{bone}{ye} searched \fcolorbox{bone}{bone}{the land}, \emph{even} forty days, each day for a year, shall \fcolorbox{bone}{bone}{ye} bear your iniquities, \emph{even} forty years, and \fcolorbox{bone}{bone}{ye} shall know my breach of promise.}
[35] \textcolor[cmyk]{0.99998,1,0,0}{I the LORD have said, I \fcolorbox{bone}{bone}{will} surely do it unto \fcolorbox{bone}{bone}{all} this evil congregation, \fcolorbox{bone}{bone}{that}  are gathered together against me: in this wilderness they shall be consumed, and there they shall die.}
[36] \textcolor[cmyk]{0.99998,1,0,0}{And the men, which Moses sent to search \fcolorbox{bone}{bone}{the land}, who returned, and made \fcolorbox{bone}{bone}{all} the congregation to murmur against him, by bringing up a slander upon \fcolorbox{bone}{bone}{the land},}
[37] \textcolor[cmyk]{0.99998,1,0,0}{Even those men \fcolorbox{bone}{bone}{that}  did bring up the evil report upon \fcolorbox{bone}{bone}{the land}, died by the plague before the LORD.}
[38] \textcolor[cmyk]{0.99998,1,0,0}{But Joshua the son of Nun, and Caleb the son of Jephunneh, \emph{which} \emph{were} of the men \fcolorbox{bone}{bone}{that}  went to search \fcolorbox{bone}{bone}{the land}, lived \emph{still}.}
[39] \textcolor[cmyk]{0.99998,1,0,0}{And Moses told these sayings unto \fcolorbox{bone}{bone}{all} the children of Israel: and the people mourned greatly.}
[40] \textcolor[cmyk]{0.99998,1,0,0}{And they rose up early in the morning, and gat them up into the top of the mountain, saying, Lo, we \emph{be} \emph{here}, and \fcolorbox{bone}{bone}{will} go up unto the place which the LORD hath promised: for we have sinned.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Moses said, Wherefore now do \fcolorbox{bone}{bone}{ye} transgress the commandment of the LORD? but it shall \fcolorbox{bone}{bone}{not} prosper.}
[42] \textcolor[cmyk]{0.99998,1,0,0}{Go \fcolorbox{bone}{bone}{not} up, for the LORD \emph{is} \fcolorbox{bone}{bone}{not} among you; \fcolorbox{bone}{bone}{that}  \fcolorbox{bone}{bone}{ye} be \fcolorbox{bone}{bone}{not} smitten before your enemies.}
[43] \textcolor[cmyk]{0.99998,1,0,0}{For the Amalekites and the Canaanites \emph{are} there before you, and \fcolorbox{bone}{bone}{ye} shall fall by the sword: because \fcolorbox{bone}{bone}{ye} are turned away from the LORD, therefore the LORD \fcolorbox{bone}{bone}{will} \fcolorbox{bone}{bone}{not} be with you.}
[44] \textcolor[cmyk]{0.99998,1,0,0}{But they presumed to go up unto the hill top: nevertheless the ark of the covenant of the LORD, and Moses, departed \fcolorbox{bone}{bone}{not} out of the camp.}
[45] \textcolor[cmyk]{0.99998,1,0,0}{Then the Amalekites came down, and the Canaanites which dwelt in \fcolorbox{bone}{bone}{that}  hill, and \fcolorbox{bone}{lime}{smote them}, and discomfited them, \emph{even} unto Hormah.}