\section{Psalm 49 Comments}

\subsection{Numeric Nuggets}
Verses 1, 8, and 13 have 13 words. Verses 6,  8, 19, and 20 have thirteen unique words. The word ``their'' is used thirteen time in the psalm. (``Their'' is used once, and ``\emph{their}'' is used once.) The 13-letter words ``understanding'' and ``understandeth'' are found in the chapter.

\subsection{Psalm 49:4}
The phrase ``dark saying'', then, is associated with parables. This is the only instance of the phrase, and the phrase ``dark sayings'' is found only twice: \begin{compactenum}
\item \textbf{Psalm 78:2} -- I will open my mouth in a parable: I will utter dark sayings of old: 
\item \textbf{Proverbs 1:6} -- To understand a proverb, and the interpretation; the words of the wise, and their dark sayings.
\end{compactenum}
It is a truth that the ear must be inclined to God to understand a parable before it can be played and sung on a harp. That is why the Psalm was called a ``parable.'' It contains a great deal more than simply warnings against living and dying without redemption or a right relationship to God. The Psalmist is an endtime Jew, when the iniquity of Israel is being paid off double (Isaiah 40:2) for his sin of rejecting the Messiah. The full payment is described in the Lamentations, and the full payment will make Hitler’s holocaust look like exactly what it was: a rehearsal (see Jeremiah 16:16, Amos 9:2). This is a saved Jew who is saying, “Wherefore should I fear in the days of evil,” because he knows how the days of evil are going to end (Matthew 24:30, Luke 21:28). Once again the “man” (verses 12, 16, 17, and 19) is a MAN (the Antichrist, see Psalm 52), and “MAN” in the aggregate. This is the forty-ninth Psalm: seven times seven, the completion of Gentile revelation.\cite{Ruckman1992Psalms}

\subsection{Psalm 49:13}
The sayings of the degenerate ``big shots'' are legend. It takes volumes to record them. They are chaff in the wind. No group of religious leaders, political leaders, educators, scientists, humanitarians, dictators, philosophers, doctors, lawyers, judges, and millionaires combined (through a period of six millenniums) could solve one major problem of mankind. There are seven:\cite{Ruckman1992Psalms}\begin{compactenum}
    \item Religious disunity.
    \item Wars between nations.
    \item Famine and starvation.
    \item Sickness.
    \item Death.
    \item Earthquakes and hurricanes.
    \item Murder and theft.
\end{compactenum}

\subsection{Psalm 49:20}
The verse makes a comparison between what God honors and what mankind honors. \cite{Ruckman1992Psalms} \begin{compactenum}
    \item Unsaved women  are called “pigs” in scripture (2 Pet. 2:22; Prov. 11:22).
    \item Unsaved men are called “dogs” (Rev. 22:15; 2 Pet. 2:22).
    \item Unsaved religious leaders are called “vipers” (Matt. 23:33).
\end{compactenum}
Psalm 49 is a self-explanatory repeat of the refrain so familiar to the reader of the Book of Ecclesiastes. \cite{Ruckman1992Psalms}\begin{compactenum}
\item You came in naked, and you go out naked (vs. 17). See  1 Timothy 6:7 and Job 1:21.
\item You can make yourself happy by “realizing” or “finding’’ yourself (vs. 18), and if you make your “bundle” before the funeral, men will praise you (vs. 18): mainly to get your money.
\item You go the way of all your flesh (vs. 19), and if they are lost like you are -— the rich man had five brothers (Luke 16:28) -— they too will die like dogs (vs. 20). You do not come up at the end of the Tribulation (vs. 14) to enter the Millennium; you stay down one thousand years, and then come up to the White Throne Judgment (Rev. 20).
\end{compactenum}