\chapter{Psalm 50}
\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{THE MIGHTY GOD}}\\ (Psalm 50) \begin{compactenum}[I.][8]
    \item  God \textbf{Speaks} \index[scripture]{Psalms!Psa 050:01} (Psa 50:1) 
    \item  God \textbf{Shines} \index[scripture]{Psalms!Psa 050:02} (Psa 50:2) 
    \item  God is not \textbf{Silent} \index[scripture]{Psalms!Psa 050:03} (Psa 50:3) 
    \item  God \textbf{States} our Errors \index[scripture]{Psalms!Psa 050:06} (Psa 50:6) 
    \item  God has \textbf{Statutes} \index[scripture]{Psalms!Psa 050:16} (Psa 50:16) 
    \item  God notices \textbf{Slander} \index[scripture]{Psalms!Psa 050:20} (Psa 50:20) 
    \item  God offers \textbf{Salvation} \index[scripture]{Psalms!Psa 050:23} (Psa 50:23) 
\end{compactenum}}
    
\marginpar{\scriptsize \centering \fcolorbox{bone}{yellow}{\textbf{GOD AT WORK}}\\ (Psalm 50) \begin{compactenum}[I.][8]
    \item  God's \textbf{Call is Continual} \index[scripture]{Psalms!Psa 050:01} (Psa 50:1) 
    \item  God's \textbf{Coming is Consuming} \index[scripture]{Psalms!Psa 050:03} (Psa 50:3) 
    \item  God's \textbf{Covenant is Required} \index[scripture]{Psalms!Psa 050:05} (Psa 50:5) 
    \item  God's \textbf{Congregation will Come Together} \index[scripture]{Psalms!Psa 050:05} (Psa 50:5) 
    \item  God's \textbf{Care is Certain} \index[scripture]{Psalms!Psa 050:15} (Psa 50:15) (for his people)
    \item  God's \textbf{Correction is Coming} \index[scripture]{Psalms!Psa 050:21} (Psa 50:21) 
    \item  God's \textbf{Character is Consistent} \index[scripture]{Psalms!Psa 050:23} (Psa 50:23) 
\end{compactenum}}



% [cmyk]{0.99998,1,0,0}{
\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://www.audioverse.org/english/audiobibles/books/ENGKJV/O/Ps/1}{\textcolor[cmyk]{0.99998,1,0,0}{Psalms Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{A Psalm of Asaph.}\\
\\
\textcolor[cmyk]{0.99998,1,0,0}{The mighty God, \emph{even} the LORD, hath \fcolorbox{bone}{lime}{spoken}, and called the earth from the rising of the sun unto the going down thereof.}\footnote{\textbf{Psalm 113:3} - From the rising of the sun unto the going down of the same the LORD’S name is to be praised.}\footnote{\textbf{Isaiah 45:5-7} -  I am the LORD, and there is none else, there is no God beside me: I girded thee, though thou hast not known me: [6] That they may know from the rising of the sun, and from the west, that there is none beside me. I am the LORD, and there is none else. [7] I form the light, and create darkness: I make peace, and create evil: I the LORD do all these things.}\footnote{\textbf{Malachi 1:11} - or from the rising of the sun even unto the going down of the same my name shall be great among the Gentiles; and in every place incense shall be offered unto my name, and a pure offering: for my name shall be great among the heathen, saith the LORD of hosts.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{Out of Zion, the perfection of beauty, God hath \fcolorbox{bone}{lime}{shined}.}\footnote{\textbf{Lamentations 2:15} - All that pass by clap their hands at thee; they hiss and wag their head at the daughter of Jerusalem, saying, Is this the city that men call The perfection of beauty, The joy of the whole earth? }
[3] \textcolor[cmyk]{0.99998,1,0,0}{Our God shall come, and shall not keep \fcolorbox{bone}{lime}{silence}: a fire shall devour before him, and it shall be very tempestuous round about him.}\footnote{\textbf{Psalm 21:9} - Thou shalt make them as a fiery oven in the time of thine anger: the LORD shall swallow them up in his wrath, and the fire shall devour them.}\footnote{\textbf{Ezekiel 15:7} - And I will set my face against them; they shall go out from one fire, and another fire shall devour them; and ye shall know that I am the LORD, when I set my face against them.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{He shall call to the heavens from above, and to the earth, that he may judge his people.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{Gather my saints together unto me; those that have made a covenant with me by sacrifice.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{And the heavens shall declare his righteousness: for God \emph{is} \fcolorbox{bone}{lime}{judge} himself. Selah.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{Hear, O my people, and I will speak; O Israel, and I will testify against thee: I \emph{am} God, \emph{even} thy God.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{I will not reprove thee for thy sacrifices or thy burnt offerings, \emph{to} \emph{have} \emph{been} continually before me.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{I will take no bullock out of thy house, \emph{nor} he goats out of thy folds.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{For every beast of the forest \emph{is} mine, \emph{and} the cattle upon a thousand hills.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{I know all the fowls of the mountains: and the wild beasts of the field \emph{are} mine.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{If I were hungry, I would not tell thee: for the world \emph{is} mine, and the fulness thereof.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{Will I eat the flesh of bulls, or drink the blood of goats?}
[14] \textcolor[cmyk]{0.99998,1,0,0}{Offer unto God thanksgiving; and pay thy vows unto the most High:}
[15] \textcolor[cmyk]{0.99998,1,0,0}{And call upon me in the day of trouble: I will deliver thee, and thou shalt glorify me.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{But unto the wicked God saith, What hast thou to do to declare my \fcolorbox{bone}{lime}{statutes}, or \emph{that} thou shouldest take my covenant in thy mouth?}
[17] \textcolor[cmyk]{0.99998,1,0,0}{Seeing thou hatest instruction, and castest my words behind thee.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{When thou sawest a thief, then thou consentedst with him, and hast been partaker with adulterers.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{Thou givest thy mouth to evil, and thy tongue frameth deceit.}
[20] \textcolor[cmyk]{0.99998,1,0,0}{Thou sittest \emph{and} speakest against thy brother; thou \fcolorbox{bone}{lime}{slanderest} thine own mother's son.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{These \emph{things} hast thou done, and I kept silence; thou thoughtest that I was altogether \emph{such} \emph{an} \emph{one} as thyself: \emph{but} I will reprove thee, and set \emph{them} in order before thine eyes.}
[22] \textcolor[cmyk]{0.99998,1,0,0}{Now consider this, ye that forget God, lest I tear \emph{you} in pieces, and \emph{there} \emph{be} none to deliver.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{Whoso offereth praise glorifieth me: and to him that ordereth \emph{his} conversation \emph{aright} will I shew the \fcolorbox{bone}{lime}{salvation} of God.}